Forecasting the 2024 U.S. Presidential Election

### 2024-10-24 paper/paper.qmd

# Create a boxplot showing the distribution of support for each candidate
ggplot(data, aes(x = candidate_name, y = pct, fill = candidate_name)) +
  geom_boxplot() +
  labs(x = "Candidate",
       y = "Percentage of Support") +
  theme_minimal() +
  theme(legend.position = "none")
```

>>>>

ggplot(data, aes(x = pct, fill = candidate_name)) +
  geom_histogram(bins = 30, alpha = 0.7, position = "identity") +
  facet_wrap(~ candidate_name) +
  labs(x = "Percentage of Support",
       y = "Count") +
  scale_fill_discrete(name = "Candidates") +
  theme_minimal() +
  theme(legend.position = "bottom")
